Supplementary material: The increasing cost of happiness

### 2021-03-12 src/draft0_word.Rmd
Major update v0.4

##### Figure 2. Posterior parameters of the dependency of happiness on income (real 2019 dollars)   
```{r get_posteriors}
income_summary <- read_rds("../results/gh9_hhoecd_data.RDS")
fits <- read_rds("../results/gh9_hhoecd_0cov_tight.RDS")

@@

##### Figure 3. Counterfactual difference in happiness between 2019 and 2001
```{r counterfactual_estimates}
fits <- read_rds("../results/gh9_hhoecd_0cov_tight.RDS")

@@

##### Figure 4. Rise in median income, change point, and population in Australia 2001-2019 
```{r figure_4, fig.width=7, fig.height=6, dpi=300}
fits <- read_rds("../results/gh9_hhoecd_0cov_tight.RDS")
income_params <- read_rds("../results/gh9_hhoecd_summary.RDS")

@@

Supplementary information is available [online](https://datarichard.github.io/The-increasing-cost-of-happiness/supplementary.html){target="_blank"}.

>>>>

##### Figure 2. Posterior parameters of the dependency of happiness on income (real 2019 dollars)   
```{r get_posteriors}
income_summary <- read_rds("../results/fits/excl_topcodes/sd/gh9_hhoecd_data.RDS")
fits <- read_rds("../results/fits/excl_topcodes/sd/gh9_hhoecd_0cov_tight.RDS")

@@

##### Figure 3. Counterfactual difference in happiness between 2019 and 2001
```{r counterfactual_estimates}
fits <- read_rds("../results/fits/excl_topcodes/sd/gh9_hhoecd_0cov_tight.RDS")

@@

##### Figure 4. Rise in median income, change point, and population in Australia 2001-2019 
```{r figure_4, fig.width=7, fig.height=6, dpi=300}
fits <- read_rds("../results/fits/excl_topcodes/sd/gh9_hhoecd_0cov_tight.RDS")
income_params <- read_rds("../results/fits/excl_topcodes/sd/gh9_hhoecd_data.RDS")

@@

Supplementary information is available [online](https://datarichard.github.io/The-increasing-cost-of-happiness/supplementary.html).

### 2021-03-12 src/supplementary0_word.Rmd
Major update v0.4

---
title: "Supplementary material: The increasing cost of happiness"
author: "R.W. Morris^1,2^, N. Kettlewell^2,3,4^  & N.Glozier^1,5^"
bibliography: ../src/references.bib
csl: ../src/elsevier-harvard.csl
output:  
  html_document:
    reference_docx: ../src/academic_style.docx
always_allow_html: yes
editor_options: 
  chunk_output_type: console
---

@@

lm_fits = read_rds(paste0(here, "results/lm_gh9_hhoecd_0cov.RDS"))

nl_fits = read_rds(paste0(here, "results/gh9_hhoecd_0cov_tight.RDS"))

@@

nl_fits_losat = read_rds(paste0(here, "results/losat_hhoecd_0cov.RDS"))

lm_fits_losat = read_rds(paste0(here, "results/lm_losat_hhoecd_0cov.RDS"))

@@

nl_fits = read_rds(paste0(here, "results/gh9_hhoecd_0cov_tight.RDS"))

nl_fits_5cov = read_rds(paste0(here, "results/gh9_hhoecd_5cov_tight.RDS"))

income_params <- read_rds("../results/gh9_hhoecd_summary.RDS")

posteriors_5c <- map_dfr(nl_fits_5cov, as.data.frame, .id = "fit") %>%
  left_join(bind_rows(income_params, .id = "fit")) %>%
  mutate(omega_dollars = (b_omega_Intercept * sd + mean)/1000) %>%
  as_tibble()

@@

posteriors_0c <- map_dfr(nl_fits, as.data.frame, .id = "fit") %>%
  left_join(bind_rows(income_params, .id = "fit")) %>%
  mutate(omega_dollars = (b_omega_Intercept * sd + mean)/1000) %>%
  as_tibble()

@@

nl_fits = read_rds(paste0(here, "results/gh9_hhoecd_0cov_tight_x0.RDS"))

log_fits = read_rds(paste0(here, "results/log_gh9_hhoecd_0cov.RDS"))

@@

nl_fits = read_rds(paste0(here, "results/gh9_hhoecd_0cov_tight.RDS"))

@@

income_params <- read_rds("../results/gh9_hhoecd_summary.RDS")

bind_rows(income_params, .id = "fit") %>%
  mutate(low = (40000 - mean)/sd,
         high = (75000 - mean)/sd) %>%
  column_to_rownames(var = "fit") %>%
  as.matrix() -> fixed_income_hash

>>>>

---
title: "Supplementary material: The increasing cost of happiness"
author: "R.W. Morris^1,2^, N. Kettlewell^2,3,4^  & N.Glozier^1,5^"
bibliography: ../src/references.bib
csl: ../src/elsevier-harvard.csl
output:  
  word_document:
    reference_docx: ../src/Rmarkdown-for-Word-styles.docx
always_allow_html: yes
editor_options: 
  chunk_output_type: console
---

@@

lm_fits = read_rds(
  paste0(here, "results/fits/excl_topcodes/sd/lm_gh9_hhoecd_0cov.RDS")
)

nl_fits = read_rds(
  paste0(here, "results/fits/excl_topcodes/sd/gh9_hhoecd_0cov_tight.RDS")
)

@@

nl_fits_losat = read_rds(
  paste0(here, "results/fits/excl_topcodes/sd/losat_hhoecd_0cov.RDS")
)

lm_fits_losat = read_rds(
  paste0(here, "results/fits/excl_topcodes/sd/lm_losat_hhoecd_0cov.RDS")
)

@@

nl_fits = read_rds(
  paste0(here, "results/fits/excl_topcodes/sd/gh9_hhoecd_0cov_tight.RDS")
)

nl_fits_5cov = read_rds(
  paste0(here, "results/fits/excl_topcodes/sd/gh9_hhoecd_5cov_tight.RDS")
)

income_summary <- read_rds("../results/fits/excl_topcodes/sd/gh9_hhoecd_data.RDS")

posteriors_5c <- map_dfr(nl_fits_5cov, as.data.frame, .id = "fit") %>%
  left_join(bind_rows(income_summary, .id = "fit")) %>%
  mutate(omega_dollars = (b_omega_Intercept * sd + mean)/1000) %>%
  as_tibble()

@@

posteriors_0c <- map_dfr(nl_fits, as.data.frame, .id = "fit") %>%
  left_join(bind_rows(income_summary, .id = "fit")) %>%
  mutate(omega_dollars = (b_omega_Intercept * sd + mean)/1000) %>%
  as_tibble()

@@

nl_fits = read_rds(
  paste0(here, "results/fits/excl_topcodes/sd/exc_zeros/gh9_hhoecd_0cov_tight.RDS")
)

log_fits = read_rds(
  paste0(here, "results/fits/excl_topcodes/sd/log_gh9_hhoecd_0cov.RDS")
)

@@

nl_fits = read_rds(
  paste0(here, "results/fits/excl_topcodes/sd/exc_zeros/gh9_hhoecd_0cov_tight.RDS")
)

@@

income_summary <- read_rds("../results/fits/excl_topcodes/sd/gh9_hhoecd_data.RDS")

bind_rows(income_summary, .id = "fit") %>%
  mutate(low = (40000 - mean)/sd,
         high = (75000 - mean)/sd) %>%
  column_to_rownames(var = "fit") %>%
  as.matrix() -> fixed_income_hash
